\section{Conclusion}

Modelling an object is a tiresome and time expensive process by nature. %
Creating variants is all the more so, considering that it requires starting over
the process as many times as necessary. %
Reevaluation mechanisms are, nowadays, increasingly frequent in parametric
systems and offer an easier way to generate variants of an object. %
A long-standing issue in CAD's field, called persistent naming, is to make sure
the operations' parameters are still valid despite their modification. %
To our knowledge, there does not seem to be such a mechanism taking advantage of
graph transformation rules available so we propose one here. %

In this paper, we take advantage of both the graph transformation rule's and
generalized map's formalisms to tackle the reevaluation mechanism task. %
Generalized maps offers an homogeneous representation of an object in all
dimensions while Jerboa's rules make possible the definition of geometric
modelling operations on which it is actually possible to perform syntactical
analysis. %
We set up a persistent naming scheme taking advantage of the Jerboa's rule. %
With this scheme, a persistent name represents a unique dart's history through
the successive involved applications and their matching nodes. %
Thus, it persistently identifies a topological parameter. %
Then, after the initial evaluation, for each persistent name an evaluation DAG
is built in order to trace an orbit's history from the bottom and up to the
orbits it originates from. %
Representing the complete history of an orbit in an evaluation DAG allows for an
efficient persistent naming mechanism that takes into account the impact of both
origins and traces modifications during reevaluation. %
Finally, reevaluation DAGs are built from top to down with evaluation DAGs and
allow matching one or more topological parameters depending on the added and/or
deleted events induced by the editing of the parametric specification. %

Jerboa proposes to define more complex rules, called scripted rules, where
several rules come one after another. %
Later works will revolve around making this reevaluation mechanism compatible
with these scripted rules. %

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
