\section{History trees}

Secondly, the topological changes (or events) an entity underwent during the
initial construction must be tracked. %
It is then necessary to trace the ``history'' leading to the registered state of
an entity designated by a persistent name within a \emph{history tree}. %

\subsection{Event nodes and Orbit nodes}

There are two types of nodes within a history tree~: \emph{event nodes} and
\emph{orbit nodes}. %
An event node is connected to at most one orbit node, is associated with an
application index and holds an event type such as a creation, a modification, a
split and so on. %
An orbit node is connected to one or more event nodes, is associated with a rule
node name and holds an orbit type. %

Within a history tree, each depth level is either a level of event nodes
(\emph{i.e.} an event level) or a level of orbit nodes (\emph{i.e.} an orbit
level). %
These levels are created alternately during the construction of any history
tree. %

\subsection{Traces and origins}

There are two kind of relationship that can exist between two nodes~: the
\emph{trace} (black arrows) or \emph{origin} (red arrows) relationships. %

The trace relationship tracks an entity identified by an orbit node up to its
previous state (another orbit node) in a history tree.

In the cases of creation, split and merging events, an entity is created, split
into several ones or several entities are merged into one. %
It is then impossible to unambiguously designate an entity without computing an
orbit of origin. %
An origin orbit is an orbit that matches all the darts used to change and
entity. %
% Dans une création et une scission, c'est l'ensemble des brins qui sont copiées
% Dans une l'ensemble des brins qui sont supprimés.

{\color{darkgreen}%
  In a copy creation event, a new entity is created from another one. %
  In this case the tree needs to track this orbit the entity originates from. %
  In a split event, several entities can appear from the result of a split. %
  Then, the tree must track the specific sub-orbit the tracked entity originates
  from. %
  Conversely, in a merging event, a tracked entity comes from several entities
  and a origin must be found. %
}

\subsection{Paths to origins}

In some cases (usually a merging event), an origin is a deleted entity, yet it
is necessary to identify them to build history trees. %
However, the operations being graph transformation rules, it is possible to
find, from the rules only, a path from an entity to its origin.
{\color{darkgreen}%
  example
}

\subsection{Example}
A history tree is built from the last known state of an entity, which will be
the root, up to the first entities it originates from, the leaves. %

The events, given the orbit type of an entity, can be deduced from a rule and a
tree is created for each persistent ID of a persistent name. %
Such a tree is built from the last known state of an entity, which will be the
tree root, up to the first entities it originates from, \emph{i.e.} the tree
leaves. %

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
