\section{Parametric specifications}

\input{../tables/parametric-specification-table}

The  reevaluation of  an  object first  requires the  recording  of its  initial
construction   ({\color{blue}modeling})  process,   \textit{i.e.}  the   applied
operations and their parameters both topological and geometric, in the form of a
parametric specification. %
In the  case of rule-based operations,  each entry must comprise  an application
ordering number (\emph{AppNumber}), a name (\emph{Name}), topological parameters
{\color{blue}as persistent names}  (\emph{TopoParameters}) and classic geometric
parameters (\emph{GeoParameters}) such as
%
\begin{equation*}
  \begin{split}
    [&AppNumber, Name, TopoParameters,\\ &GeoParameters]
  \end{split}
\end{equation*}
%
is a syntactic example of a parametric specification entry. %

A parametric specification registers topological parameters in order to allow
the reevaluation of an object. %
This is a two-part task, namely the persistent identification of darts and the
persistent naming of topological parameters. %

\subsection{Persistent ID}

% What is a PI ?
\emph{Persistent IDs} (or \emph{PIs}) are part of the persistent naming scheme
proposed in this contribution. %
This structure describes any dart by recording all the rules that affected it
during a construction. %
A PI must also be unique in order to avoid ambiguity in a Persistent Name. %

% Why is a PI needed ?
As suggested in Section~\ref{ssec:g-maps}, a dart is the topological entity of
lowest dimension in a G-map and is part of several orbits. %
Since darts result from the application of rules, to use them in a persistent
naming scheme means they must be persistently identified.%
%
% How PIs are built ?
In order to describe the state of a dart at any time during a construction, a PI
records an \textit{AppNumber} and a node name (\emph{NodeName}). %
Upon the application of a rule, although a node matches one or more darts, a
dart is matched by at most one node. %
Thus, for each application that affected a dart $d$, a PI must record the name
of the node that matched $d$ such that
%
\begin{equation*}
  \begin{split}
    PI_{d} = [AppNumber &- NodeName;\\ AppNumber &- NodeName;\\ &\dots\\
    AppNumber &- NodeName]
  \end{split}
\end{equation*}
%
is a syntactic example of a PI associated to $d$. %

% How can a PI be unique ?
A PI, by construction, is unique. %
When a rule has an empty left member, each node creates exactly one dart and
each of the associated PI is \textit{de facto} unique. %
From this point on, any future PI will either be an update or a creation derived
from the PI of an already existing dart. %
And because of the former PIs being unique, any subsequent PI is unique. %

% {\color{darkgreen} See Fig.~\ref{fig:demo-fig-triangulation-left-match}, dart
%   $a_{0}$ persistent ID is $1 — n_{6}$ because it has been created without copy
%   by the node $n_{6}$ of the first rule application. %
%   However it has been updated after the application of the face triangulation
%   rule Fig.~\ref{fig:rule-face-triangulation}. Its new persistent ID is now
%   $1 — n_{6}; 2 – n_{0}$ as it has been matched by the node $n_{0}$ of the
%   second rule application.} %

\subsection{Persistent Names}

A \emph{Persistent Name} (or \emph{PN}), is a structure which describes, with a
collection of PIs, all the changes that affected an orbit in order to use it as
a topological. %
Due to the mechanism of rule application, a topological parameter is actually a
dart and not an orbit. %

Although a PI can reliably identify a dart, it may not be able, by itself, to represent all the changes that affected an orbit. %

In such a case, a PN will collect one or more PIs until there is as necessary
and sufficient amount of data to precisely describe an orbit as a topological
parameter such that
%
\begin{equation*}
  PN_{a} = \{PI_{x} \dots PI_{z}\}
\end{equation*}
%
is a syntactic example of a PN. %
%
% Although darts have persistent IDs, a topological entity comprises several. %
% A single persistent ID may not suffice to represent all the rules that impacted
% such an entity. %
% The gathering of enough persistent IDs within a persistent name can then be
% necessary to persistently and formally designate a topological entity. %
% A persistent name is created a posteriori of an application. %
% It is a collection of one or more persistent IDs found in an entity. %
% It must comprises a minimum of persistent IDs and these persistent IDs must
% represent a maximum of rule application with as little overlap as possible. %
% On souhaite représenter une entité topo avec un maximum d'information
% d'évolution tout en ne prenant que le nécessaire en PIs.

\subsection{Example}

{\color{darkgreen}%
  Table~\ref{tbl:param-spec-example} illustrates the construction of a
  parametric construction. %
  The create-square rule, of ID 1, creates a square ex-nihilo and, thus, does not
  need any topological parameter. %
  However, the next entry, namely extrude-face of ID 2, as its name suggests
  extrude a face into a volume. %
  A persistent name, $PN_{1}$, is created in order to identify the face to be
  extruded. %
  Firstly, the rule expects a face as a parameters so the orbit type of the entity
  must be $\orbit{\alpha 0, \alpha 2}$. %
  Secondly, the entity to match must have a persistent ID being $1n_{0}$. %
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
