\section{Conclusions and perspectives}
\label{sec:conclusion}

Event tracking is one of the core functionalities of geometric modeling kernels.
The tracked events serve a variety of purposes such as building a construction history or avoiding ambiguities in persistent naming of entities for model reevaluation.
In this paper, we propose a new method to statically detect topological events.
Analysing an operation code to precisely identify which events can be statically detected is a very difficult task. To overcome this situation, we represent objects models with generalized maps and their geometric operations with Jerboa's graph transformation rules
The generalized maps allow us to represent any topological entities such as face vertices or face edges and to define all relationships between these entities.
Jerboa's rules can be syntactically analysed in order to detect topological events independently from any specific object.
They also have the immediate advantage that the events can be precomputed which result in a noticeable time reduction to detect these events at runtime.

Through a set of scenarios, we have shown the efficiency of the static event detection compared to dynamic methods.

This approach leads the way towards future works.
Firstly, as of now, the operations that can be analysed are defined with a single rule. An improvement will be to adapt this method to higher level operations defined with scripts which combine several rules.
Secondly, most current persistent naming methods rely on the tracking of topological entities evolutions. Working on a complex model, or in case of frequent reevaluations of parametric models, the static tracking of topological entities should allow a significant improvement of the efficiency of persistent naming methods. This could be accurately evaluated by integrating this static tracking into parametric systems.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
