\documentclass[../main.tex]{subfiles}

\begin{document}
\section[Event detection]{Event detection}
\label{sec:event-detection}

\subsection[Creation]{Creation}
\label{sec:creation}

Given the face triangulation rule and a given an orbit $n_{2}$·$\orbit{1,2}$.
% Avant/après de la triangulation
% surligner le sommet créé

After the rule's \highlight{application} we can observe a vertex has been created at the
center of the face.

In the rule this vertex is associated with the node $n_{2}$.

The node $n_{2}$ does not exist in the left member of the rule but is described
in the right member.

Because a rule can only modify what has been \highlight{filtered} then $n_{2}$
is created.

\subsection[Split]{Split}
\label{sec:split}

Given the face triangulation rule and a given an orbit $n_{0}$·$\orbit{0,1}$.
% Avant/après de la triangulation
% surligner le sommet créé

After the rule's application we can observe the square face has been splitted
into four triangular faces.

In the rule the faces are associated with the entirety of the rule's right
member.

And darts filtered in left are splitted between each resulting faces.

Unlike the $n_{0}$ in the rule's left member, the $2^{nd}$ \highlight{implicit
  link} in $n_{0}$ in the rule's right member is missing.

Because the darts of $n_{0}$ which were previously linked by $\alpha-1$
($2^{nd} implicit links$) are not linked with an $i$-link ($i \in \orbit{0,1}$)
then the face has been splitted.




\subsection[Merge]{Merge}
\label{sec:merge}



\end{document}
