\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Main concepts}

\subsection[Generalized Maps]{Generalized maps}
\label{sec:generalized-maps}

G-Maps, as stated in\cite{marcheix2018persistent}, intuitively represent the
decomposition of $n$-dimensional objects according to the successive dimensions
of their boundaries, the different parts being linked by relationships noted
$\alpha i$.

\begin{definition}[Orbit]

  Let $G = (V, E, s, t, \alpha)$ topological graph of dimension $n$, $o$ a
  subset of $[0, n]$ and $v$ a node of $G$.

  The orbit $G\orbit{o}(v)$, incident to $v$ and of type $\orbit{o}$ (or
  $\orbit{o}$-orbit), is the sub-graph of $G$ containing $v$ and the nodes of
  $G$ reachable through edges labeled in $\orbit{o}$ as well as these edges.

  When there is no ambiguity about the considered graph $G$ the orbit is written
  $\orbit{o}$·$v$.
\end{definition}

\begin{itemize}
	\item vertex is of type $\orbit{\alpha 1, \alpha 2}$,
  \item edge is of type $\orbit{\alpha 0, \alpha 2}$,
  \item face is of type $\orbit{\alpha 0, \alpha 1}$
\end{itemize}


\subsection[Graph transformation rules]{Graph transformation rules}
\label{sec:graph-transf-rules}

Since G-Maps are graphs we use graph transformation rules, or \emph{rules}, as
modeling operations. Intuitively, given two G-Maps $G$ and $H$, a rule, written
$L \longrightarrow R$, describes the transformation of a sub-graph of $G$ with a
scheme $L$ into a sub-graph of $H$ with a scheme $R$.

A scheme being an abstract layer on graphs, they contain labeled nodes used to
match sub-graphs.

A rule node $n$ of label $l(n)$ matches a set of darts and their
$\alpha i$-links if they are in $l(n)$.

We consider two different types of $\alpha i$-links within a scheme. First
\emph{explicit links}. These links connects rule nodes together allowing to
match a connected component within a sub-graph. Second \emph{implicit links}.
These links connect together the darts matched by any node $n$ and implicitly
express those links by having their $\alpha i$ in $l(n)$, hence implicit links.

Rule nodes can be considered created, deleted or preserved. A node is a
\emph{created node} $n$ if it only exists in $R$, i.e. if $n \in R \setminus L$.
A node is \emph{deleted node} $n$ if it only exists in $L$, i.e. if
$n \in L \setminus R$. Finally, a node is a \emph{preserved node} $n$ if it
exists in both $L$ and $R$, i.e. if $n \in L \cap R$.

\begin{definition}[Complete orbit]
  Let $r : L \longrightarrow R$ be a rule, $n$ a node such that $n \in L$ and
  $\orbit{o}$ an orbit type.

  $L\orbit{o}(n)$ is a \emph{complete orbit} if and only if for all node
  $n'\in L\orbit{o}(n)$, $n'$ filters either implicitly or explicitly all
  dimensions in $\orbit{o}$, i.e. for all dimensions $i \in \orbit{o}$, $n'$ is
  either the source of an $\alpha i$-link or $i \in l(n')$.

\end{definition}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
