%% This is file `cag-template.tex',
%%
%% Copyright 2018 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%%
%% $Id: cag-template.tex 151 2018-11-22 04:42:39Z rishi $
%%
%% Use the options `twocolumn,final' to obtain the final layout
%% Use `longtitle' option to break abstract to multiple pages if overfull.
%% For Review pdf (With double line spacing)
%\documentclass[times,twocolumn,review]{elsarticle}
%% For abstracts longer than one page.
%\documentclass[times,twocolumn,review,longtitle]{elsarticle}
%% For Review pdf without preprint line
%\documentclass[times,twocolumn,review,nopreprintline]{elsarticle}
%% Final pdf
%\documentclass[times,twocolumn,final]{elsarticle}
%%
\documentclass[times,twocolumn,final]{els-format/elsarticle}
%%


%% Stylefile to load CAG template
\usepackage{els-format/cag}
\usepackage{framed,multirow}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{latexsym}

% Following three lines are needed for this document.
% If you are not loading colors or url, then these are
% not required.
\usepackage{url}
\usepackage{xcolor}
\definecolor{newcolor}{rgb}{.8,.349,.1}

\usepackage{hyperref}

\usepackage[switch,pagewise]{lineno} %Required by command \linenumbers below
\usepackage{adjustbox}
\usepackage{float}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{subfiles}
\usepackage{subcaption}

\graphicspath{{./els-format/} {./figures/}}
\include{commands.tex}

\journal{Computers \& Graphics}

\begin{document}

\verso{Preprint Submitted for review}

\begin{frontmatter}

\title{Static detection of topological changes in geometric modeling operations}%

\author[1]{Maxime \snm{Gaide}\corref{cor1}}
\cortext[cor1]{Corresponding author:
  % Tel.: +0-000-000-0000;
  % fax: +0-000-000-0000;
}
\emailauthor{maxime.gaide@ensma.fr}{Maxime Gaide}
%\ead{example@email.com}

\author[2]{David \snm{Marcheix}}
% \fntext[fn1]{Footnote 1.}

\author[3]{Agnès \snm{Arnould}}
\author[3]{Xavier \snm{Skapin}}
\author[3]{Hakim \snm{Belhaouari}}
\author[2]{Stéphane \snm{Jean}}

\address[1]{ISAE-ENSMA Poitiers, Université de Poitiers, LIAS, Poitiers, France}
\address[2]{Université de Poitiers, ISAE-ENSMA Poitiers, LIAS, Poitiers, France}
\address[3]{Université de Poitiers, Univ. Limoges, CNRS, XLIM, Poitiers, France}

%\received{1 February 2017}
\received{\today}
%%%% Do not use the below for submitted manuscripts
%\finalform{28 March 2017}
%\accepted{2 April 2017}
%\availableonline{15 May 2017}
%\communicated{S. Sarkar}

\begin{abstract}
  Advanced geometric modelers require the detection of topological changes
  caused by modeling operations on objects such as face splitting or volume
  merging. Therefore, modeling kernels APIs generally give access to this data
  which is obtained by tracking the topological changes. Such a tracking is
  dynamically performed by comparing topological cells (vertices, edges, faces,
  volumes) before and after each modification, which can be very time consuming.

  In this article, we propose a method to statically detect topological changes.
  We rely on the formalization of geometric models and their operations:
  generalized maps and graph transformation rules. A syntactical analysis of
  such rules allows to compute, statically before run time, the changes that
  will affect topological entities. We also characterize the situations where it
  is impossible to state that an entity has been split or merged and, thus,
  entails some local dynamic verification. A cost comparison of both
  methods, classical dynamic and proposed static, with standard modeling
  operations make it possible to estimate time savings.
\end{abstract}

% \begin{abstract}
% %%%
% \lipsum[1]
% %%%%
% \end{abstract}

\begin{keyword}
  \KWD Topology-based modeling\sep Topological change detection\sep Static analysis\sep Graph
  transformation rules\sep Generalized maps
\end{keyword}

\end{frontmatter}

\linenumbers

%%main text
\subfile{parts/introduction}
\subfile{parts/main-concepts}
\subfile{parts/contribution}
\subfile{parts/comparison}
\subfile{parts/conclusion}

\bibliographystyle{els-format/cag-num-names}
\bibliography{references}
\end{document}

